Supermartingales and Termination Analysis of Statistical PCF

### 2021-01-18 LICS21/notes.tex
Merge branch 'master' of https://github.com/4Denthusiast/prob-programming-termpaper Sec. I: tweak

AKR: {I'd suggest, as a simplified version of the non-affine continuous example, $(\tY \lambda f x. (\mathsf{let} \; e = \tsample \; \mathsf{in} \; \tif{e \leq p}{x}{f^2(x+1) \oplus_{sig(x)} f^3(x+1)}) \underline 0$ (or possibly that, but with some simpler algebraic function instead of the sigmoid). This removes the extra $\oplus$ and makes $x$ more relevant, but I think it preserves all the important features.}

>>>>

AKR: {I'd suggest, as a simplified version of the non-affine continuous example, $(\tY \lambda f x. (\mathsf{let} \; e = \tsample \; \mathsf{in} \; \tif{e \leq p}{x}{f^2(x+1) \oplus_{sig(x)} f^3(x+1)}) \, \underline 0$ (or possibly that, but with some simpler algebraic function instead of the sigmoid). This removes the extra $\oplus$ and makes $x$ more relevant, but I think it preserves all the important features.}
